Generating Synthetic Data

### 2023-02-02 sections/data_preprocessing/real_world_data.qmd
uh

```python
from sklearn.datasets import fetch_california_housing
df, y = fetch_california_housing(return_X_y=True, as_frame=True)
df["target"] = y.values
data_path = "dev/artifacts/upload/data/real_world"
import os
if not os.path.isdir(os.path.join(data_path,"raw")):
    os.makedirs(os.path.join(data_path,"raw"))
df.to_csv(os.path.join(data_path,"raw/cal_housing.csv"), index=False)
```

>>>>

```{.python}
from sklearn.datasets import fetch_california_housing
df, y = fetch_california_housing(return_X_y=True, as_frame=True)
df["target"] = y.values
data_path = "dev/artifacts/upload/data/real_world"
import os
if not os.path.isdir(os.path.join(data_path,"raw")):
    os.makedirs(os.path.join(data_path,"raw"))
df.to_csv(os.path.join(data_path,"raw/cal_housing.csv"), index=False)
```
